---
title: "EDA Customer Purchase Journey Prediction"
author: "SumbarajuAditya"
date: "1/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(reshape2)
library(ggplot2)
library(grid)
library(gridExtra)
library(data.table)
library(forecast)
library(xts)
```

## Including Plots

Loading dataset from four input files

```{r}
df.TFDNov <- read.csv("C:/BU/DSC680/project1/data/D11", header = T, sep = ";", 
    stringsAsFactors = FALSE)
df.TFDDec <- read.csv("C:/BU/DSC680/project1/data/D12", header = T, sep = ";", 
    stringsAsFactors = FALSE)
df.TFDJan <- read.csv("C:/BU/DSC680/project1/data/D01", header = T, sep = ";", 
    stringsAsFactors = FALSE)
df.TFDFeb <- read.csv("C:/BU/DSC680/project1/data/D02", header = T, sep = ";", 
    stringsAsFactors = FALSE)
DNov_cols <- colnames(df.TFDNov)
DDec_cols <- colnames(df.TFDDec)
DJan_cols <- colnames(df.TFDJan)
DFeb_cols <- colnames(df.TFDFeb)
identical(DNov_cols, DDec_cols)
identical(DNov_cols, DJan_cols)
identical(DNov_cols, DFeb_cols)
df.TFD0 <- rbind(df.TFDJan, df.TFDFeb)
df.TFD1 <- rbind(df.TFDNov, df.TFDDec)
df.TFD_FullSet <- rbind(df.TFD0, df.TFD1)
```
```{r}
TFcols <- c("DateTime", "CustID", "Age_cat", "ResArea", 
    "ProdSub", "ProdID", "Cost", "Asset", "SalesPrice")
colnames(df.TFD_FullSet) <- TFcols
dt.TF <- as.data.table(df.TFD_FullSet)
dt.TF$DateTime <- as.POSIXct(dt.TF$DateTime)
dt.TF$ProdID <- as.factor(dt.TF$ProdID)
df.TFD_FullSet$DateTime <- as.POSIXlt(df.TFD_FullSet$DateTime)
df.TFD_FullSet$Age_cat = as.factor(df.TFD_FullSet$Age_cat)
df.TFD_FullSet$ResArea = as.factor(df.TFD_FullSet$ResArea)
df.TFD_FullSet$CustID = as.factor(df.TFD_FullSet$CustID)
df.TFD_FullSet$ProdSub = as.factor(df.TFD_FullSet$ProdSub)
```

top selling products

```{r}
dt.TF_prodid <- dt.TF[, list(TotAmount = sum(Cost)), 
    by = list(DateTime, ProdID, ResArea)]
topPr <- dt.TF_prodid[, list(Total = sum(TotAmount)), 
    by = .(ProdID)]
topPr <- topPr[order(-Total)]
head(topPr)
```

```{r}
ggplot(topPr[Total >= 2700, ]) + geom_bar(aes(x = ProdID, 
    y = Total, fill = ProdID), stat = "identity", alpha = 0.8) + 
    theme(axis.text.x = element_text(angle = 25)) + 
    scale_fill_hue(l = 40)
```

Number Products Sold per Day

```{r}
dt.TF_prodid <- dt.TF[, list(TAmount = sum(Cost)), 
    by = list(DateTime, ProdID, ResArea)]
dt.TF_prodidtop3 <- subset(dt.TF_prodid, ProdID %in% 
    c(4714981010038, 4710421090059, 4711271000014))
dt.TF_prodid_nores <- dt.TF[, list(TAmount = sum(Cost)), 
    by = list(DateTime, ProdID)]
dt.TF_prodid1 <- subset(dt.TF_prodid_nores, ProdID == 
    4714981010038)
dt.TF_prodid2 <- subset(dt.TF_prodid_nores, ProdID == 
    4710421090059)
dt.TF_prodid3 <- subset(dt.TF_prodid_nores, ProdID == 
    4711271000014)
ggplot(dt.TF_prodidtop3[, list(TAmount), by = list(DateTime, 
    ProdID)]) + geom_bar(aes(x = DateTime, y = TAmount, 
    fill = ProdID), stat = "identity", alpha = 0.8) + 
    scale_fill_manual(values = c("#007F85", "#BD3828", 
        "#AB00B6")) + labs(y = "Sales", x = "")
```
```{r}
dt.TF_trans <- unique(dt.TF[, list(DateTime, CustID, 
    ResArea)])
df.trans <- dt.TF_trans[, list(num_trans = length(CustID)), 
    by = DateTime]
ts_trans <- xts(df.trans$num_trans, as.Date(df.trans$DateTime))
attr(ts_trans, "frequency") <- 7
trans_decom <- stl(as.ts(ts_trans), s.window = "periodic", 
    t.window = 7)
plot(trans_decom)
```
# Sales per Region observations
Splitting the data into regions shows the difference in the number of transactions in each Region.
1. Region E being the busiest region with the highest number of sales. 
2. Regions A and B can be seen to have low numbers of sales. Most Regions show a similar sales profile for all three top products 
3. Region G shows the highest number of sales for Product 4710421090059 where as this product is recorded least sales in other regions.

```{r}
ggplot(dt.TF_prodidtop3[, list(num_trans = sum(TAmount)), 
    by = list(ProdID, ResArea)]) + geom_bar(aes(x = ProdID, 
    y = num_trans, fill = ProdID), stat = "identity", 
    alpha = 0.8) + scale_fill_manual(values = c("#007F85", 
    "#BD3828", "#AB00B6")) + facet_wrap(~ResArea) + 
    labs(y = "Sales", x = "") + theme(axis.ticks = element_blank(), 
    axis.text.x = element_blank())

```

